Communication complexity: Chapter 6 \\ One-way communication and simultaneous message passing

### 2019-02-15 CS860-CommunicationComplexity/assignments/Chapter6.tex
Solved up to last two

@@

>>>>

\begin{proof}
Let $\pi$ be a two-way deterministic protocol computing $f$, and achieving cost $D(f)$. We construct a one-way protocol $\pi'$ for $f$ as follows. Alice considers the sub-tree of the protocol tree $\pi$ corresponding to what she would send on her input, and all of Bob's possible replies. The size of this sub-tree is at most $2^{D(f)}$. After reading this sub-tree, Bob outputs the bit at the leaf to which his input with Alice's communication corresponding.
\end{proof}

@@

\begin{proof}
Consder any randomized one-way protocol $\pi$ which solves $\Disj$.. We will construct a protocol for $\Index$ of the same cost, and apply the lower bound from the previous section to obtain the result. Let $x \in \{0,1\}^n$ and let $y \in [n]$ be Alice and Bob's respective inputs to $\Index$. They run their $\Disj$ oracle $\pi$ as if Alice input were $x$ and Bob's was the standard basis vector $e_y\in\{0,1\}^n$, where only the $y$-th bit $e_y$ is $1$. Since
$$\Disj(x,e_y) = \Index(x,y)$$ 
this protocol solves $\Index$ using the same communication cost as $\pi$.
\end{proof}
